---
title: "p8105_hw1_np2619"
author: "Nidhi Patel"
date: "9/22/2020"
output: github_document
---

```{r, results = FALSE}

library(tidyverse)

```


## Problem 1

```{r hw1_prob1}
prob1_df = 
  tibble(
    samp = rnorm(10),
    vec_log = samp > 0,
    vec_char = c("I", "do", "not", "know", "if", "I", "am", "doing", "this", "right"),
    vec_fac = factor(c("orange", "yellow", "purple", "purple", "yellow", "orange", "purple", "purple", "yellow", "orange"))
)

mean_samp = mean(pull(prob1_df, samp))

mean_log = mean(pull(prob1_df, vec_log))


str(prob1_df)

#mean_char = mean(pull(prob1_df, vec_char))
#mean_fac = mean(pull(prob1_df, vec_fac))

```
The mean cannot be taken for character or factor vectors as they are not numeric or logical. However, the mean can be taken for the random sample and logical vector (sample >0). In the logical vector, it appears TRUE = 0 and FALSE = 1. 

(To be clear, I wrote the characters before I watched the live video, I think I did it correctly after watchinf the video!)

### Problem 1, continued

```{r, results = FALSE}

prob1_df$vec_log <- as.numeric(as.factor(prob1_df$vec_log))

mean_log = mean(pull(prob1_df, vec_log))

#prob1_df$vec_char <- as.numeric(prob1_df$vec_char)
#NA introduced by coercion error for the line above

prob1_df$vec_fac <- as.numeric(prob1_df$vec_fac)

mean_fac = mean(pull(prob1_df, vec_fac))

```

Using the as.numeric function, vec_log and vec_fac convert to numeric. Using the same function, vec_char was not converted, but introduced NAs.

### Problem 1, continued again.
Converting and multiplying.

```{r, results = FALSE}
prob1_df

prob1_df$samp * as.numeric(prob1_df$vec_log)

as.factor(prob1_df$vec_log) * prob1_df$samp

as.numeric(as.factor(prob1_df$vec_log)) * prob1_df$samp

#str(prob1_df)

```
I converted the logical vector to numeric and multiplied it by the sample. I was unable to multiply the logical--> factor vector by the sample. The factor levels were "TRUE" and "FALSE", which cannot be multiplied.  When the logical--> factor vector was converted to numeric, I was able to multiply it by the sample. There is a difference in the result because the direct conversion of logical-> numeric resulted in "TRUE" = 1 and "FALSE" = 0, but after converting logical to numberic by way of factor, "TRUE" = 2 and "FALSE" = 1.


## Problem 2 


```{r prob2}

data("penguins", package = "palmerpenguins")

#drop_na_(pull(penguins, flipper_length_mm))

#completerecords <- na.omit(penguins)
#drop_na(flipper_length_mm)
#mean(penguins, flipper_length_mm)


#plot_penguins = tibble(
  #x = bill_length_mm,
 # y = flipper_length_mm
 # )
#this doesn't work yet ://

#ggplot(plot_penguins, aes(x = x, y = y, color = species)) + geom_point()

#mean_flip = mean(pull(penguins, flipper_length_mm))
#This data set has `r nrow(penguins)` observations and `r ncol(penguins)` vectors.  There are 4 factor variables (species, island, sex, year), 4 numeric vectors (bill length, bill depth, flipper length, body mass). The mean length of penguin flippers is `r mean_flip`.

```


 

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
#plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
